\documentclass[12pt,letterpaper]{article}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{fullpage}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{paralist}
\usepackage{color}
\usepackage[nottoc]{tocbibind}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{soul}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\oddsidemargin 0mm
\evensidemargin 0mm
%\textwidth 160mm
%\textheight 200mm
%\renewcommand\baselinestretch{1.0}
\pagestyle {plain}
\pagenumbering{arabic}
\newcounter{stepnum}



\title{\parbox{\linewidth}{\centering Problem Statement \endgraf\bigskip Version\#: 1}}
\author{\parbox{\linewidth}{\bigskip \centering Group\#: 38 \endgraf\bigskip Team Name: Binary \endgraf\bigskip Members: \endgraf\bigskip Tongfei Wang : wangt62 \endgraf\bigskip Bowen Yuan : yuanb1 \endgraf\bigskip Tim Zhang : zhangj14}}
\date{\parbox{\linewidth}{\bigskip\bigskip \centering \today\endgraf\bigskip SFWR ENG 3XA3 \endgraf\bigskip McMaster University}}


\begin {document}
\maketitle
\newpage

\section{Introduction}


\tab Tetris is a tile-matching puzzle game. “Tetriminos” are differently shaped blocks and they drop from the top of the screen one by one. The player can move or rotate the Tetriminos as they fall. The goal of this game is to create a horizontal line without gaps. Once the line is created, it will disappear and be replaced by the blocks above it.The purpose of the game is to bring the joy back to the players who love it.



\section{Importance}


\tab	Game occupies a great part of many people's leisure time, and lately, it becomes much more so with a rising use of gaming devices. However, as there are numerous games to choose, Tetris is no longer a good choice for people. Once upon a time, this classical game earned its fans with the unique play style. Currently, with the burst of technology, many new games come to the world with their fascinating theme and attractive scene, which pushes Tetris out of the age.  As a result, it is essential to modify the game to make it more competitive.


\section{Context}


\tab	To achieve the goal, we are going to add the new features like an internal economic system, experience system, item system and special Tetriminos” to increase the complexity. When deleting a line, a certain amount of “gold” and “experience” will be awarded to the player. \st{The experience unlocks high-level items while the players can buy the items by the gold they earned. Moreover, there will be more different shapes of Tetriminos in our game as to make the game a little more challenging.} Some of the Tetriminos will have a certain type, such as bomb-type, wall-type, double-gold-type and so on. Every type has its own different function when they are deleted.These features will bring another perspective to value the gameplay for the players.

\tab Stakeholders for this game are video game players, group members, Tetris fans. {\color{red}Video game players are the potential user of the game. Group members contribute in developing the game.Tetris fan will be the major user of the game. TA and professor will provide the advise and critical judgement.}It is being coded in JavaScript, It will allow users to play the game for free and without any installation. {\color{red} It will be uploaded to a server to allow the player assess it everywhere has a computer with interest connected. It is design to open in every major browser such as IE, Chrome etc...}
After our recreation of the Tetris, the players will enjoy playing it again.











\end{document}